\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{array}

\section*{Framework B$'$ — Symbolic Breath Cycle}

\subsection*{Core Purpose}

Framework B$'$ introduces the concept of \textbf{Breath-State Encoding} — a dynamic logic system that oscillates between symbolic expansion and contraction, modeled after the inhale/exhale cycle of breath.

While Framework A defines \emph{where} a symbolic state lives, Framework B$'$ defines \emph{how} that state changes — via harmonic cycles.

\subsection*{Breath as Logic}

In Base13Log42, ``breath'' is a \textbf{cyclic transformation principle} embedded into symbolic progression:
\begin{itemize}
  \item \textbf{Inhale}: symbolic expansion (forward recursion into higher shells)
  \item \textbf{Exhale}: symbolic contraction (reset or return to equilibrium)
  \item \textbf{Pause}: the zero-state, $Z = 0$, symbolic stillness
\end{itemize}

\subsection*{Breath-Cycle Phases}

\begin{center}
\begin{tabular}{|c|c|c|}
\hline
\textbf{Phase} & \textbf{Symbolic Action} & \textbf{State Shift} \\
\hline
Inhale & Expansion, forward recursion & $x \rightarrow x + 1$ \\
Peak   & Tension, overflow approaching & $x \rightarrow S_k'$ \\
Exhale & Contraction, symbolic compression & $x \rightarrow x - 1$ \\
Pause  & Z = 0 equilibrium reset & $x = \dot{0}$ \\
\hline
\end{tabular}
\end{center}

Each shell contains a breath loop encoded via its positional range. Symbolic states ``breathe'' through recursion, not linearity.

\subsection*{Breath-State Intensity}

For a symbolic state $x$ in shell $k$, define:

\[
b_k(x) = \frac{x - S_{k-1}'}{S_k' - S_{k-1}'}
\]

This maps $x$ to a unit interval $[0, 1]$:
\begin{itemize}
  \item $b_k(x) \approx 0$: inhale start
  \item $b_k(x) = 0.5$: breath peak
  \item $b_k(x) \approx 1$: exhale end → triggers overflow to next shell
\end{itemize}

\subsection*{Symbolic Breath Oscillator}

Define the breath-state oscillator as:

\[
\beta(x) = \sin(2\pi b_k(x))
\]

This function governs:
\begin{itemize}
  \item \textbf{Breath-State Intensity} — amplitude of symbolic pressure
  \item \textbf{Symbolic Velocity} — rate of resonance change (used in Framework C)
\end{itemize}

\subsection*{Symbolic Reset (Z = 0)}

When $x > S_k'$, the system resets via overflow:

\[
x \rightarrow \dot{0} \rightarrow S_{k+1}' + 1
\]

This creates harmonic rebirth: a symbolic return to zero before expanding into the next tier.

\subsection*{Framework B$'$ Summary}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Category} & \textbf{Description} \\
\hline
Name & Symbolic Breath Cycle \\
Phase Encoding & Inhale / Exhale / Pause \\
Breath Intensity & $b_k(x) = \frac{x - S_{k-1}'}{S_k' - S_{k-1}'}$ \\
Oscillator Function & $\beta(x) = \sin(2\pi b_k(x))$ \\
Reset Symbol & $\dot{0}$ (symbolic pause or anchor) \\
Logic Role & Harmonic control of symbolic recursion \\
Depends On & Framework A (Positional Hierarchy) \\
Feeds Into & Framework C (Resonance Logic) \\
\hline
\end{tabular}
\end{center}

\subsection*{Interpretation}

Framework B$'$ transforms symbolic logic into rhythmic motion. Rather than advancing linearly, the system follows a sinusoidal cycle — \emph{breathing} logic into and out of recursive shells.

This forms the temporal and harmonic basis for all resonance logic to follow.
