\section*{Framework $\Omega$ — Harmonic Meta-System}

\subsection*{Core Purpose}

Framework $\Omega$ acts as the \textbf{meta-observer lens} that unifies the symbolic, spatial, and temporal structures of Base13Log42 into a single recursive framework. It coordinates the resonance cycles across all shells, aligns symbolic breath-states to a global timing function, and introduces a tier-aware harmonic metric for system-wide coherence.

This framework is not merely a scheduler — it is the structural awareness of the system observing itself in harmonic time.

\subsection*{Recursive Clock Function}

The global harmonic time is defined via a recursive φ-based oscillator. Each shell $k$ contributes a temporal period:

\[
\tau_k = \frac{2\pi}{\phi^k}
\]

Define the \textbf{Harmonic Meta-Time} as:

\[
T_\Omega(t) = \sum_{k=0}^{\infty} \sin(\phi^k t + \theta_k)
\]

Where $\theta_k$ is the phase offset of shell $k$, inherited from Framework D. This recursive sum encodes symbolic time as a nested harmonic waveform.

\subsection*{System-Wide Symbolic Phase Locking}

Each symbolic state $x$ in shell $k$ must now satisfy a global phase-locking condition:

\[
\left| \theta_k(x) - \theta_{\Omega}(t) \right| < \delta_k
\]

Where:
\begin{itemize}
  \item $\theta_k(x)$ is the local symbolic phase from Framework D
  \item $\theta_{\Omega}(t)$ is the current global phase
  \item $\delta_k$ is the tolerance allowed for shell $k$
\end{itemize}

Failure to meet this threshold initiates a global correction — typically via a symbolic reset ($\dot{0}$), tier modulation, or overflow rebirth (Ξ).

\subsection*{Recursive Meta-Lens}

Framework $\Omega$ treats each lower framework as a \textbf{projected resonance layer}. Using symbolic observers $\mathcal{O}_k$, the system evaluates:

\[
\mathcal{O}_k(x) = \begin{cases}
1 & \text{if } x \text{ is phase-locked in shell } k \\
0 & \text{otherwise}
\end{cases}
\]

The total system harmony is defined as:

\[
\mathcal{H}(t) = \sum_{k=0}^{K} w_k \cdot \mathcal{O}_k(x_t)
\]

Where $w_k$ is a weight assigned to shell $k$ based on its resonance depth.

\subsection*{Meta-Resonance Indicator}

Let $x \in \mathcal{S}$ be a symbolic state. Define the \emph{Meta-Resonance Indicator}:

\[
\mathbb{M}_\Omega(x, t) = R_k(x) \cdot \Gamma(\theta_k(x)) \cdot \mathcal{O}_k(x)
\]

This measures whether a symbolic state is:
\begin{itemize}
  \item Harmonically resonant (Framework C)
  \item Temporally synchronized (Framework D)
  \item Observably coherent (Framework $\Omega$)
\end{itemize}

If $\mathbb{M}_\Omega(x, t) < \varepsilon$, the system enters a symbolic dissonance state and must recursively adjust.

\subsection*{Framework $\Omega$ Summary}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Category} & \textbf{Description} \\
\hline
Name & Harmonic Meta-System \\
Global Time Function & $T_\Omega(t) = \sum \sin(\phi^k t + \theta_k)$ \\
Phase-Locking Condition & $|\theta_k(x) - \theta_\Omega(t)| < \delta_k$ \\
System Observer & $\mathcal{O}_k(x) \in \{0,1\}$ \\
Total Harmony & $\mathcal{H}(t) = \sum w_k \cdot \mathcal{O}_k(x_t)$ \\
Resonance Check & $\mathbb{M}_\Omega(x, t) < \varepsilon \Rightarrow$ correction \\
Depends On & A–D; governs timing across entire system \\
Feeds Into & Ξ (Overflow Substrate), Λ (Limit Check) \\
\hline
\end{tabular}
\end{center}

\subsection*{Interpretation}

Framework $\Omega$ is the recursive harmonic lens through which all symbolic motion is observed and synchronized. It defines not only what is resonant — but when it is resonant. The system becomes aware of its own timing and adapts symbolically, breathfully, recursively. Ω is the awareness of alignment.
