\section*{Framework A — Fractal Positional Hierarchy}

\subsection*{Core Purpose}

Framework A defines the \textbf{positional structure} of the Base13Log42 system. It introduces a recursively expanding numeric hierarchy that partitions the positive integers into nested “shells,” each increasing exponentially in size. This creates a scaffold for all symbolic states, forming the base on which resonance, breath-state, and overflow logic are later defined.

\subsection*{State Space}

The system operates on the positive natural numbers:
\[
\mathcal{S} = \mathbb{N}^+ = \{1, 2, 3, 4, \dots\}
\]
Note: the value $0$ is \emph{not} used as a number — it is reserved for symbolic reset as $\dot{0}$ in later frameworks.

\subsection*{Shell Definition}

Each shell $k$ is defined by its upper bound:

\[
S_k' = 13^{k+1} - 1 \quad \text{for } k \geq 0
\]

This produces an exponential growth of shell size:

\begin{center}
\begin{tabular}{|c|c|c|}
\hline
\textbf{Shell Level ($k$)} & \textbf{Range} & \textbf{Ends at $S_k'$} \\
\hline
0 & $1$ to $12$ & $12$ \\
1 & $13$ to $168$ & $168$ \\
2 & $169$ to $2196$ & $2196$ \\
3 & $2197$ to $28560$ & $28560$ \\
\hline
\end{tabular}
\end{center}

The shell $k$ includes the state interval:
\[
\mathcal{S}_k = \left(S_{k-1}',\ S_k'\right]
\]

\subsection*{Recursive Shell Positioning}

Given a symbolic state $x \in \mathcal{S}$, its shell level $k$ is determined by the smallest $k$ satisfying:
\[
x \leq S_k'
\]

Its \textbf{shell-local position} is:
\[
\text{offset}_k(x) = x - S_{k-1}'
\]

This defines its phase location within the shell and is used later for breath-state and resonance calculations.

\subsection*{Symbol Set}

The Base13Log42 system uses a 13-symbol alphabet:
\[
\{ \dot{0},\ 1,\ 2,\ 3,\ 4,\ 5,\ 6,\ 7,\ 8,\ 9,\ A,\ B,\ C \}
\]

\begin{itemize}
  \item $1$–$9$ are standard decimal digits.
  \item $A$, $B$, $C$ represent values $10$, $11$, $12$ respectively.
  \item $\dot{0}$ represents a symbolic reset or breath pause — not a numeric zero.
\end{itemize}

\subsection*{Recursive Variant (Optional Form)}

In some symbolic constructions, shell sizes are recursively defined using:

\[
S_0 = 3,\quad S_k = 3 \cdot S_{k-1} + 7
\]

This produces a growth curve:

\begin{center}
\begin{tabular}{|c|c|}
\hline
\textbf{$k$} & \textbf{$S_k$} \\
\hline
0 & 3 \\
1 & 16 \\
2 & 55 \\
3 & 172 \\
4 & 523 \\
5 & 1576 \\
\hline
\end{tabular}
\end{center}

This alternate recursion may be used for symbolic resonance scaling or non-uniform shell definitions.

\subsection*{Framework A Summary}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Category} & \textbf{Description} \\
\hline
Name & Fractal Positional Hierarchy \\
Symbol Set & $1$–$9$, $A$–$C$; $\dot{0}$ as symbolic reset \\
Shell Formula & $S_k' = 13^{k+1} - 1$ \\
Role & Base positional structure for symbolic logic \\
Recursion Use & Nested, exponential tiering \\
Feeds Into & B$'$ (Breath-State), C (Resonance), $\Lambda$ (Overflow) \\
\hline
\end{tabular}
\end{center}

\subsection*{Interpretation}

Framework A defines the spatial skeleton of Base13Log42. Each state lives in a shell, which determines how it breathes (Framework B$'$) and resonates (Framework C). It is purely numeric — no resonance, phase, or breath dynamics are applied here — but it anchors all of them structurally.
