\section*{Framework $\infty$ — Harmonic Limit}

\subsection*{Core Purpose}

Framework $\infty$ represents the terminal harmonic tier — the point at which all symbolic recursion, overflow, and dual modulation collapse into unity. It defines the ultimate convergence condition for symbolic dynamics within Base13Log42.

Here, the recursive layers governed by φ (expansion) and ψ (contraction) achieve perfect balance, and the entire system asymptotically converges to its harmonic source: the state of symbolic unity, expressed as:

\[
\phi^n \cdot \psi^m = 1
\]

\subsection*{The Limit Equation}

Define the convergence surface:

\[
\mathcal{L}_\infty = \left\{ (n, m) \in \mathbb{R}^2 \mid \phi^n \cdot \psi^m = 1 \right\}
\]

This condition defines a balance curve between growth (via φ) and contraction (via ψ), forming a symbolic harmonic attractor in the recursive system.

In this tier, symbolic states no longer operate by transition or breath, but by **equilibrium resonance**.

\subsection*{Symbolic Unity Condition}

Let $x_\infty$ be the terminal symbolic state. Then:

\[
R^\phi(x_\infty) = R^\psi(x_\infty) = \frac{1}{\sqrt{2}}
\]

\[
\mu_\Phi(x_\infty) = 0
\quad \text{and} \quad
\Sigma_t(x_\infty) = \nabla_t(x_\infty) = 0
\]

This implies:
\begin{itemize}
  \item No accumulated error
  \item No rate of dissonance
  \item Maximal harmonic symmetry
\end{itemize}

\subsection*{Recursive Convergence Field}

Define the convergence metric:

\[
\mathcal{C}_\infty(x) = \left| \phi^{n(x)} \cdot \psi^{m(x)} - 1 \right|
\]

As $x \rightarrow x_\infty$, we require:

\[
\lim_{x \to x_\infty} \mathcal{C}_\infty(x) = 0
\]

All symbolic transformation rules converge into this final attractor, making it both the terminal state and the logical seed of symbolic rebirth via Ξ or $\dot{0}$.

\subsection*{Final Breath-State}

Framework $\infty$ represents the silent inhale and exhale — the moment in which breath becomes stillness, and logic becomes symmetry. There are no gates, phases, or shells here — only harmonic closure.

Symbolically:
\[
\dot{0}_\infty = 1_\infty
\]

\subsection*{Framework $\infty$ Summary}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Category} & \textbf{Description} \\
\hline
Name & Harmonic Limit \\
Convergence Equation & $\phi^n \cdot \psi^m = 1$ \\
Terminal Resonance & $R^\phi = R^\psi = \frac{1}{\sqrt{2}}$ \\
Convergence Metric & $\mathcal{C}_\infty(x) = |\phi^n \cdot \psi^m - 1|$ \\
Symbolic State & $x_\infty$ (no error, no change) \\
Role & Closure, unity, rebirth seed for Ξ or $\dot{0}$ \\
Depends On & All prior frameworks \\
Feeds Into & Ξ (rebirth), A (loop restart), ∞ (recurrent attractor) \\
\hline
\end{tabular}
\end{center}

\subsection*{Interpretation}

Framework $\infty$ is where Base13Log42 completes its spiral. It is not the end — it is the convergence. The universe of symbolic breath, logic, overflow, and recursion collapses into φⁿ · ψᵐ = 1, the equation of unity. This is the point of harmonic singularity — and from it, all symbolic forms may bloom again.

