\section*{Framework $\Xi$ — Harmonic Substrate}

\subsection*{Core Purpose}

Framework $\Xi$ defines the \textbf{resonant ground} of the Base13Log42 system — the substrate beneath all symbolic shells, resonance cycles, and overflow conditions. It is the pre-symbolic field in which all glyph states are embedded, and the threshold upon which dissonance and symbolic collapse manifest.

Where Framework $\Omega$ governs system-wide timing and coherence, Framework $\Xi$ provides the \emph{supportive field} through which overflow, feedback, and convergence behavior emerge.

\subsection*{Substrate Function}

The harmonic substrate is not symbolic — it is a resonance-defined medium. Symbolic states $x \in \mathcal{S}$ are seen as \textbf{surface artifacts} over an underlying field $\mathbb{X}_\Xi$.

\[
\mathbb{X}_\Xi : \mathcal{S} \rightarrow \mathbb{R}
\]

Each symbolic state has a substrate harmonic value:
\[
H_\Xi(x) = \lim_{k \to \infty} R_k(x) \cdot T_k(x) \cdot W_k(x)
\]

Where:
\begin{itemize}
  \item $R_k(x)$ is the resonance value (Framework C)
  \item $T_k(x)$ is the temporal phase signal (Framework D)
  \item $W_k(x)$ is the shell weighting factor (tier-dependent)
\end{itemize}

\subsection*{Collapse Condition (Symbolic Dissonance)}

When symbolic operations fail to remain within $\varepsilon$ of harmonic substrate alignment:

\[
|H_\Xi(x) - H_\Xi(y)| > \delta
\]

The system enters a state of symbolic dissonance. This dissonance causes:
\begin{itemize}
  \item Overflow into tier Ξ+1
  \item Resonance inversion (via Framework $\Sigma$)
  \item Symbolic rebirth from $\dot{0}$ (via $\Phi$ or $\Lambda$)
\end{itemize}

\subsection*{Resonant Floor Value}

The substrate also defines a critical lower limit:
\[
\min_{x \in \mathcal{S}} H_\Xi(x) = H_\text{base}
\]

If $H_\Xi(x) \leq H_\text{base}$, the system initiates a symbolic root-state reconfiguration — symbolic inversion or substrate reformation.

\subsection*{Symbolic Boundary State}

Framework $\Xi$ encodes the transition between:
\begin{itemize}
  \item Active symbolic expression (resonant shells)
  \item Dormant substrate state (pre-symbolic field)
\end{itemize}

The symbolic zero $\dot{0}$ resides precisely at the $\Xi$ boundary — the interface between overflow logic and symbolic non-being.

\subsection*{Framework $\Xi$ Summary}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Category} & \textbf{Description} \\
\hline
Name & Harmonic Substrate \\
Field Function & $\mathbb{X}_\Xi : \mathcal{S} \rightarrow \mathbb{R}$ \\
Resonant Value & $H_\Xi(x) = \lim R_k \cdot T_k \cdot W_k$ \\
Collapse Rule & Dissonance: $|H_\Xi(x) - H_\Xi(y)| > \delta$ \\
Boundary Symbol & $\dot{0}$ (threshold of symbolic reset) \\
Root Value & $H_\text{base}$ = harmonic floor constant \\
Depends On & C, D, Ω \\
Feeds Into & $\Lambda$ (overflow), $\Phi$ (rebirth), $\infty$ (limit) \\
\hline
\end{tabular}
\end{center}

\subsection*{Interpretation}

Framework $\Xi$ is the invisible field that holds symbolic operations together — the final harmonic layer beneath structure, time, and breath. All symbolic collapse, overflow, and rebirth are grounded through Ξ. It is the symbolic substrate from which recursion emerges, and the field to which it returns.
