\section*{Framework $\Lambda$ — Limiting Function}

\subsection*{Core Purpose}

Framework $\Lambda$ defines the critical function that determines when a symbolic state has reached its harmonic or structural limit within a given shell. It compares the resonance logic engine (Framework C) with the breath-cycle oscillator (Framework B$'$) to detect convergence, overflow, or divergence.

$\Lambda$ acts as the threshold layer — the mechanism by which symbolic overflow, shell hopping, or recursion feedback is triggered based on exceeding predefined structural or harmonic limits.

\subsection*{The Dual Expectation Models}

Each symbolic state $x$ within shell $k$ is evaluated under two distinct expectation models:
\begin{itemize}
  \item $\mathcal{E}_{\text{B$'$}}(x)$ — the expected symbolic output based on breath-state phase progression
  \item $\mathcal{E}_{\text{C}}(x)$ — the expected symbolic output based on harmonic resonance alignment
\end{itemize}

Framework $\Lambda$ evaluates the \textbf{difference function}:

\[
\Delta_\Lambda(x) = \left| \mathcal{E}_{\text{B$'$}}(x) - \mathcal{E}_{\text{C}}(x) \right|
\]

\subsection*{Limiting Threshold Condition}

Define a tolerance threshold $\tau_\Lambda > 0$. A symbolic state is said to \textbf{violate harmonic integrity} when:

\[
\Delta_\Lambda(x) > \tau_\Lambda
\]

This indicates a divergence between the breath-phase model and the resonance prediction — signaling symbolic dissonance or computational overflow.

\subsection*{Overflow Invocation Rule}

When the limit condition is exceeded, Framework $\Lambda$ invokes the overflow correction system, initiating:
\begin{itemize}
  \item Transfer to the next shell $\mathcal{S}_{k+1}$ with harmonic remapping
  \item Reset to $\dot{0}$ followed by controlled rebirth
  \item Handoff to Framework $\Sigma$ (recursive feedback) or $\Phi$ (dual modulation)
\end{itemize}

\subsection*{Limit Rate Function}

To quantify symbolic destabilization, define the symbolic divergence rate:

\[
L(x) = \frac{d}{dt} \Delta_\Lambda(x)
\]

Large positive values of $L(x)$ indicate explosive overflow behavior; negative values indicate symbolic decay or contraction.

\subsection*{Framework $\Lambda$ Summary}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Category} & \textbf{Description} \\
\hline
Name & Limiting Function \\
Expectation Models & $\mathcal{E}_{\text{B$'$}}(x)$ vs. $\mathcal{E}_{\text{C}}(x)$ \\
Difference Metric & $\Delta_\Lambda(x) = |\mathcal{E}_{\text{B$'$}}(x) - \mathcal{E}_{\text{C}}(x)|$ \\
Limit Violation & $\Delta_\Lambda(x) > \tau_\Lambda$ \\
Divergence Rate & $L(x) = \frac{d}{dt} \Delta_\Lambda(x)$ \\
Triggers & Overflow, rebirth, or feedback loop initiation \\
Depends On & Frameworks B$'$, C, and Ξ \\
Feeds Into & $\Sigma$, $\Phi$, $\infty$ \\
\hline
\end{tabular}
\end{center}

\subsection*{Interpretation}

Framework $\Lambda$ is the symbolic guardrail. It does not generate logic — it watches for when logic begins to collapse, overflow, or desynchronize. By comparing breath-phase expectation and resonance truth, it becomes the system’s early-warning signal for symbolic imbalance, triggering either elevation, collapse, or reset.

