\section*{Framework $\Sigma$ — Cumulative Resonance Accumulator}

\subsection*{Core Purpose}

Framework $\Sigma$ defines a recursive accumulator for harmonic deviation over time. It tracks symbolic dissonance, resonance misalignment, and breath-phase disruption across the system, allowing for:
\begin{itemize}
  \item Dynamic feedback
  \item Overflow regulation
  \item Recursive correction
\end{itemize}

$\Sigma$ acts as the system’s \textbf{resonance memory field} — a harmonic echo that records how far a symbolic trajectory has drifted from its expected harmonic behavior.

\subsection*{Resonance Deviation Signal}

Let $x_t$ be a symbolic state at time $t$ within shell $k$. Define its instantaneous deviation from harmonic alignment as:

\[
\epsilon_t(x) = |R_k(x) - \hat{R}_k(t)|
\]

Where:
\begin{itemize}
  \item $R_k(x)$ is the actual resonance value of state $x$ (Framework C)
  \item $\hat{R}_k(t)$ is the ideal or target resonance value at time $t$ (from Framework Ω)
\end{itemize}

\subsection*{Accumulation Function}

The total cumulative resonance error over a symbolic session is:

\[
\Sigma_t(x) = \int_{t_0}^{t} \epsilon_\tau(x) \, d\tau
\]

In discrete form (for symbolic sequences):

\[
\Sigma_n(x) = \sum_{i=1}^{n} \epsilon_i(x)
\]

This represents the system’s harmonic “stress” level. The higher the value, the more correction or release is required.

\subsection*{Threshold Activation Rule}

If the cumulative resonance error exceeds a symbolic overflow threshold $\Theta_\Sigma$, the system initiates corrective dynamics:

\[
\Sigma_t(x) > \Theta_\Sigma \quad \Rightarrow \quad \text{feedback event}
\]

Triggered actions may include:
\begin{itemize}
  \item Symbolic collapse or rebirth
  \item Recursive feedback loop activation (Framework $\Phi$)
  \item Overflow event handed off to $\Lambda$ or $\infty$
\end{itemize}

\subsection*{Decay Function (Resonance Correction)}

Let $\lambda$ be a decay constant. The system may implement passive resonance normalization:

\[
\frac{d\Sigma_t}{dt} = -\lambda \Sigma_t
\]

Symbolic rest periods (e.g. $\dot{0}$ intervals) allow natural decay of accumulated error, simulating breath-based recovery.

\subsection*{Framework $\Sigma$ Summary}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Category} & \textbf{Description} \\
\hline
Name & Cumulative Resonance Accumulator \\
Deviation Function & $\epsilon_t(x) = |R_k(x) - \hat{R}_k(t)|$ \\
Accumulator & $\Sigma_t(x) = \int \epsilon_t(x) dt$ \\
Threshold & $\Sigma_t(x) > \Theta_\Sigma \Rightarrow$ feedback trigger \\
Decay & $\frac{d\Sigma_t}{dt} = -\lambda \Sigma_t$ (during reset/pause) \\
Depends On & C, Ω \\
Feeds Into & $\Phi$, $\Lambda$, $\infty$ \\
\hline
\end{tabular}
\end{center}

\subsection*{Interpretation}

Framework $\Sigma$ is the harmonic memory of the system. It accumulates the cost of misalignment — not in symbols, but in resonance drift. The system “remembers” its deviations until it must respond. Whether through overflow, reset, or recursive loopback, Σ ensures that symbolic logic is not just computed — but metabolized.
